---
output: github_document
---
<!-- badges: start -->
[![R-CMD-check](https://github.com/rmcgill777/ebatools/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/rmcgill777/ebatools/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ebaTools

`ebaTools` provides functions for evidence-based assessment of diagnostic
tests. The package includes tools for calculating diagnostic accuracy
statistics, performing Bayesian updating, interpreting likelihood ratios,
and visualizing results with a Fagan nomogram.

## Installation

### CRAN

```r
install.packages("ebaTools")
```

### Development version

```r
# install.packages("remotes")
remotes::install_github("rmcgill777/ebaTools")
```

## Example

```{r}
library(ebaTools)

# Calculate diagnostic accuracy statistics
stats <- eba_stats(
  tp = 45,
  fp = 12,
  fn = 5,
  tn = 138
)

stats

# Update pretest probability using likelihood ratios
results <- bayes_update(
  pretest_probability = 0.30,
  lr_positive = 6,
  lr_negative = 0.25
)

results

# Interpret the positive post-test probability
eba_interpretation(
  post_probability = results$post_positive
)

# Create a Fagan nomogram
fagan_nomogram(
  pretest_probability = 0.30,
  lr_positive = 6,
  lr_negative = 0.25
)
```

## Main Functions

| Function | Description |
|----------|-------------|
| `eba_stats()` | Calculate diagnostic accuracy statistics from a 2 × 2 contingency table. |
| `bayes_update()` | Update disease probability using Bayes' theorem and a likelihood ratio. |
| `eba_interpretation()` | Provide an evidence-based interpretation of likelihood ratios. |
| `fagan_nomogram()` | Visualize Bayesian updating with a Fagan nomogram. |
